Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-30 papers/contact/paper.tex
changed one word!!! Tests skipped!

The $g_\sigma^A$ correlation function in each configuration is very
flat, with only small, smooth changes as the surface is approached.
Our functional $g_\sigma^A$ very closely matches the Monte Carlo
predictions in each case, while that of Gross consistently
underestimates the correlation at the interface by
\textcolor{red}{several percent}.  We note that the theoretical curves
extend into the region from which the fluid is excluded.  This value
corresponds to the correlation function that would be observed in the
vanishingly unlikely scenario in which there was a sphere present at
that location.  Naturally, we are unable to observe this quantity in
our Monte Carlo simulations.

>>>>

The $g_\sigma^A$ correlation function in each configuration is very
flat, with only small, smooth changes as the surface is approached.
Our functional $g_\sigma^A$ very closely matches the Monte Carlo
predictions in each case, while that of Gross consistently
underestimates the correlation at the interface by a significant margin.  We note that the theoretical curves
extend into the region from which the fluid is excluded.  This value
corresponds to the correlation function that would be observed in the
vanishingly unlikely scenario in which there was a sphere present at
that location.  Naturally, we are unable to observe this quantity in
our Monte Carlo simulations.
